Extended Data

### 2021-11-16 doc/manuscript/Dow_Extended_Data.Rmd
review Extended Data Fig. 2

![**Extended Data Figure 2 | Phenological patterns of forest canopy greenness (top row) and stem growth of ring- and diffuse-porous trees, represented as both relative and cumulative fractions of total annual growth (middle and bottom rows, respectively), at our two focal study sites** In the top row, canopy greenness is characterized using the two band Enhanced Vegetation Index (EVI2) ..., with each line representing a year between 2000 and 2018. For stem growth, each line represents one year's growth for a given tree, fit with McMahon model.](tables_figures/growth_curves_all.png){ width=100% }

@@

![**Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest.** Shown are matrices of linear coefficients of first-order linear regressions between temperature and $DOY_{25}$, where Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (ring-porous: May 5 at SCBI, May 13 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black circles indicate the critical $T_{max}$ window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF).](tables_figures/climwin_figure.png){ width=70% }

>>>>

![**Extended Data Figure 2 | Phenological patterns of forest canopy greenness (top row) and stem growth of ring- and diffuse-porous trees, represented as both relative and cumulative fractions of total annual growth (middle and bottom rows, respectively), at the Smoithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** In the top row, canopy greenness is characterized using the two band Enhanced Vegetation Index (EVI2), with each line representing a year between 2000 and 2018. For stem growth, each line represents the growth of one tree over one year, as modeled based on a five-parameter logistic growth model to dendrometer band data.](tables_figures/growth_curves_all.png){ width=100% }

@@

![**Extended Data Figure 3 | Landscapes of relationships between the day of year on which 25% of annual growth is achieved ($DOY_{25}$) and temperature in prior weeks for ring- and diffuse-porous trees at the Smoithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are matrices of linear coefficients of first-order linear regressions between temperature and $DOY_{25}$, where Window Open and Window Close indicate number of weeks prior to $DOY_{25}$ (ring-porous: May 5 at SCBI, May 13 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black circles indicate the critical $T_{max}$ window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF).](tables_figures/climwin_figure.png){ width=70% }
